### 2020-05-17 writeup/transfer.tex
sec 3.2

The proof of Proposition \ref{prop_data_size} is similar to Proposition \ref{prop_dist_transition}.
We compare the model shift bias and the amount of reduced variance of $\hat{\beta}_t^{\MTL}$.
An intuitive interpretation of Proposition \ref{prop_data_size} is that:
i) If the two task models are sufficiently similar (as specified under the first bullet), adding the source task always provides positive transfer;
ii) Otherwise, as we increase the number of source task data points, the transfer is positive initially, but transitions to negative eventually.

@@

\begin{proposition}\label{prop_data_efficiency}
\end{proposition}

>>>>

The proof of Proposition \ref{prop_data_size} is similar to Proposition \ref{prop_dist_transition}.
We compare the model shift bias and the amount of reduced variance of $\hat{\beta}_t^{\MTL}$.
An intuitive interpretation of Proposition \ref{prop_data_size} is that:
i) If the two task models are sufficiently similar (as specified under the first bullet), adding the source task always provides positive transfer;
ii) Otherwise, as we increase the number of source task data points, the transfer is positive initially, but transitions to negative eventually.
We leave the proof of Proposition \ref{prop_data_size} to Appendix \ref{app_proof_data}.

@@

\begin{proposition}\label{prop_data_efficiency}
	In the setting of Example \ref{ex_basic}, assume that $c_1 = c_2 = c > ??$ and $d^2 \le {2\sigma^2} /{(p c)}$.
	Then the data efficiency ratio is equal to $\frac{1}{2c} + \frac{\sigma^2}{2\sigma^2 - p d^2 c / 2}$.
\end{proposition}
Note that we have stated the result assuming that $c_1 = c_2$.
Similar results can also be obtained when they are different.
We omit the details.
The proof of Proposition \ref{prop_data_efficiency} can be found in Appendix \ref{app_proof_data}.
